\documentclass{article}

\author{Angus Griffith}
\title{Summer Research Scholarship Report}

\usepackage{url}

\begin{document}
\section{Upper and Lower Bounds for Normal Derivatives of Dirichlet Eigenfunctions}
\cite{HT02}

\section{Upper and Lower Bounds for Boundary Values of Neumann Eigenfunctions}
\cite{BHXX}

\section{Boundary Quasi-Orthogonality and sharp inclusion bounds for large Dirichlet Eigenvalues}
\cite{BH11}

\section{Fast computation of high-frequency Dirichlet eigenmodes}
\cite{BH14}

\section{Examples: Dirichlet eigenvalues}

\begin{thebibliography}{9}

\bibitem[HT02]{HT02}
Hassell. A and Tao, T.
\textsl{Upper and lower bounds for boundary values of Neumann eigenfunctions}.
Math. Res. Lett. Vol. 9 (3), 2002. % 289 -- 305

\bibitem[BH]{BHXX}
Barnett, A.H. and Hassell. A.
\textsl{Upper and lower bounds for boundary values of Neumann eigenfunctions}.
In preparation, 2015.

\bibitem[BH11]{BH11}
Barnett, A.H. and Hassell, A.
\textsl{Boundary quasi-orthogonality and sharp inclusion bounds for large Dirichlet eigenvalues}.
SIAM J. Numer. Anal. Vol. 49 (3), 2011.

\bibitem[BH14]{BH14}
Barnett, A.H. and Hassell, H.
\textsl{Fast Computation of High-Frequency Dirichlet Eigenmodes via Spectral Flow of the Interior Neumann-to-Dirichlet Map}.
Comm. Pure Appl. Math. Vol 67, 2014.

\bibitem[MPSpack]{MPS}
Barnett A. and Betcke T.
mpspack,
\textsl{A MATLAB toolbox to solve Helmholtz PDE , wave scattering and eigenvalue problems using particular solutions and integral equations},
Version 1.33-dev, 2014.
Available online: \url{https://code.google.com/p/mpspack/}

\end{thebibliography}
\end{document}
